%For future reference: the command to get rid of the preceding spaces is \setlength{\parindent}{0pt}
\documentclass[12pt]{extarticle}
\usepackage[margin=3cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage[rm,light]{roboto}

\title{\vspace{-2cm}\texttt{swan\_hack} \\ {Code of Conduct}\vspace{-1cm}}
\date{}
\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlength{\parskip}{12pt}


\begin{document}
	\maketitle
	In line with the aims of swan\_hack, the purpose of this document is to ensure a welcoming and safe environment to anyone and everyone who might take an interest, at any level of skill. 
	
	\section*{General Rules}
	The following is a list of general rules and guidelines we ask members to adhere to when at meets and interacting with each other online. Violation of these rules or other activity deemed as offences to the aims of swan\_hack are listed in the \emph{Tiers of Offences} section.
    \textbf{The final say as to what is and is not permitted at meets and online is reserved for the committee.}
    
	\begin{itemize}
		\item Behaviour that resembles bullying or harassment in any form will not be tolerated under any circumstances. Offences in this category are considered Tier 3 or Tier 4 offences immediately.
		\item While it is often inevitable for a discussion to turn into a heated one, committee reserves the right to ask both parties to calm down or change topic.
		\item Be friendly and welcoming to new members. If someone doesn't have as much as experience as you in a certain area, encourage and share resources with them that you found useful.
		\item Don't make anything that could cause physical injury. Explosions and fast moving objects aside, lasers or rapid flashing lights can be harmful all the same. If you are planning on doing something spectacular please clear with those around you first, and be mindful of what you might take for granted.
		\item The opinion of one individual does not represent the opinion of the entire community.
		\item Please keep your projects within the laws of the United Kingdom (to a reasonable extent).
	\end{itemize}   
	
	\section*{Offence Tiers}
	After a violation of the above rules or other activity deemed as an offence to the aims of swan\_hack, the committee reserves the right to decide which tier the offence belongs to, depending on its severity. 
	
	Committee members have executive right to execute any of the following actions immediately, and then notify all other committee members. If enough committee members deem that the action was unjustified, then the action will be reversed and apology issued. 
	
	The tiers, their descriptions and their associated committee actions are listed below.
	\begin{itemize}
	    \item Tier 1 - Minor offences. Results in a request from a committee in relation to a recent activity.
	    \item Tier 2 - Request from Tier 1 ignored or other offences deemed by a committee member to be of enough concern. Results in a server-wide mute of a specified length, notified through a direct message.
	    \item Tier 3 - Request from Tier 1 ignored, offence from Tier 2 repeated or other offences deemed by a committee member to be of enough concern. Results in a ban from the swan\_hack Discord server.
	    \item Tier 4 - Same as Tier 3, but includes offences outside of the swan\_hack Discord server. Results in a ban from the society. 
	\end{itemize}
	    
	\footnotesize Last changed: December 2021 

\end{document}

